---
title: "Covid-19 Florida Data by County"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: ["twitter"]
    source_code: https://github.com/chol3ra/BST692FlexDashboard
date: "`r Sys.Date()`"
runtime: shiny
---

<style>
.navbar {
  background-color: #15dcb2ff;
  border-color: #15dcb2ff
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    background-color: #c35dca;
    color: white;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: #c35dca;
}
.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #c35dca;
}
.navbar-inverse .navbar-collapse,
.navbar-inverse .navbar-form {
  border-color: #c35dca;
}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(knitr)
library(readr)

us_counties <- read_csv("us-counties.csv", 
    col_types = cols(date = col_date(format = "%Y-%m-%d")))
saveRDS(us_counties, file = "fl_counties.rds")

fl_counties <- filter(us_counties, state == "Florida")

```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

